### 2018-04-23 papers/synth/intro.tex
asd

%Motivate VTS
Eukaryotic cells, including human cells, consists of multiple compartments.
%
Vesicle Traffic Systems(VTSs) are the material transport mechanisms
among the compartments inside the eukaryotic cells~\cite{vtsIntro}.
%
Almost all subsystems of eukaryotic cells depend on VTSs.
%
Therefore, understanding how VTSs functions is one of the key
questions of cell biology.
%
In this paper, we are looking at the computational questions 
arise from the VTSs.
%
In the following, we use the model of VTSs that has been presented
in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.

% Describe VTS in detail
While molecules are transported by VTSs, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active along in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
compartment.
%
Not all the pairs of molecules can participate in the fusion, it is
usually determined by wet experiments the potential fusion pairs.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
Since a molecule has to be active in order to participate in fusion,
the molecule may be present in the other places without being active
and does not interfere with regulation of the other fused
channel-compartment pairs.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecule in a compartment or
channel may make the active or inactive.
%
We call this regulation as {\em activity functions}.

% Defending our model
%
In the VTS model, we assume that the system is in study state and
the concentrations of the molecules do not change over time.
%
Therefore, the system only has aspects of a network or a graph.
%
We model the system as a labelled graph, where compartments are nodes and
transport channels are edges.
%
The set of molecules present and their activity in a compartment or
a channel is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing matrix
containing Boolean values for each pair of molecules and activity
Boolean functions.
%
Since the system is in study state, we expect that any molecule that
leaves a compartment must come back via some path on the graph.
%
We call this property of VTS as {\em stability}.

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means patch work of wet experiments~\cite{model} for
identifying the compartments, channels, molecules, their activity, and
regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system.
%
The search for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%
For example, we suspect that some edges are missing from the graph, since
we expect the must satisfy stability.
%
Due the combinatorial nature of graphs, the search space is huge and often
hard to enumerate naively.
%
We need specialized methods to perform the search.

%
We may translate the problem into a synthesis question, in which 
we have a partial system  and a given property that
the system needs to satisfy.
%
The synthesis method completes the system such that the property
is satisfied by it.
%

In synthesis, we may have a partial

\ashu{Make a case for expected properties!!}
Furthermore, it is a matter of debate what properties the VTSs should
have, such as stability, i.e., every chemical that is leaving a
compartment comes back.

\ashu{Speculative: Make a case for completing partial parts of VTSs!!}

The constraints discussed on the VTSs that allow a VTS to be feasible
are combinatorial in nature, for example stability or 3-connectedness.
%
The problem of synthesizing parts of a VTS that are unobserved such that 
the modified VTS

It is appropriate that we translate 
We turn the problem of synthesizing parts of 
%
We consider several versions of the synthesis problem involving different
parts of VTSs that can be synthesized, such as modifying labels,
adding/deleting edges, learning activity functions, and adding nodes.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into a satisfiability of
QBF with uninterpreted Boolean functions.

Since an available,

on the labels.

There are several constraints that limits

There are several constraints that encode the interaction.

The labels on the nodes

>>>>

%Motivate VTS
Eukaryotic cells, including human cells, consists of multiple compartments.
%
Vesicle Traffic Systems(VTSs) are the material transport mechanisms
among the compartments inside the cells~\cite{vtsIntro}.
%
Almost all subsystems of the cells depend on VTSs.
%
Therefore, understanding how VTSs functions is one of the key
questions of cell biology.
%
In this paper, we are looking at the computational questions 
arise from the VTSs.
%
In the following, we use the model of VTSs that has been presented
in~\cite{VTS}.
%
Please look at appendix~\ref{sec:model}
for the detailed discussion on pros and cons of the model.

% Describe VTS in detail
While VTSs transports molecules, VTSs are also
regulated by the molecules.
%
Each compartment contains a set of molecules.
%
The molecules are transported to the other compartments via
unidirectional channels.  
%
The molecules in a compartment may be active or not active.
%
Similarly, a molecule can be active in a channel. 
%
The active molecules are the regulators of the channels.
%
A channel is enabled by a pair of molecules
such that one occurs in the channel and the other
occurs in the destination compartment.
%
Both the molecules must be active in the channel
and compartment respectively.
%
The pairs are called {\em fusing} molecules and analogously
the channel is considered to be {\em fused} with the
destination compartment.
%
Not all the pairs of molecules can participate in the fusion, it is
usually determined by wet experiments the potential fusion pairs.
%
To ensure effective regulation, the fusing molecule pairs must be
unique for each fused channel-compartment pair.
%
A molecule that have participated in a fusion must not interfere
with fusion at different compartments or channels.
%
Therefore, the molecule must be inactive in appropriate compartments.
%
The activity of molecules is regulated by the other molecules, i.e.,
the presence and absence of the other molecule in a compartment or
channel may make the active or inactive.
%
We call this regulation as {\em activity functions}.

% Defending our model
%
In the VTS model, we assume that the system is in study state and
the concentrations of the molecules in the compartments do not change over time.
%
We model the system as a labelled graph, where compartments are nodes and
transport channels are edges.
%
The set of molecules present and their activity in a compartment or
a channel is the label of the respective node or edge.
%
The regulation controls are defined by a fusion pairing matrix
containing Boolean values for each pair of molecules and activity
Boolean functions.
%
Since the system is in study state, we expect that any molecule that
leaves a compartment must come back via some path on the graph.
%
We call this property of VTS as {\em stability}.

% Partial info defence
%
Although the VTSs are important, our understanding of VTSs are partial.
%
It largely means the patch work of wet experiments~\cite{model} for
identifying the compartments, channels, molecules, their activity, and
regulatory control.
%
Often the information is scattered around in several publications.
%
Even after with some effort we may collate all the known information about
a VTS, we may still have unknown pieces of the system.
%
%{Speculative: Make a case for completing partial parts of VTSs!!}
%
For example, we may suspect that some edges are missing in a VTS that
does not satisfy the stability condition.
%
The synthesis for the unknown pieces may be {\em assisted} by computation on
the graph model of VTSs.
%

In this paper, we consider several versions of the synthesis problem
involving different parts of VTSs that can be synthesized, such as
modifying labels, adding/deleting edges, learning activity functions,
and adding nodes.
%
We also consider variation on the properties against which we do synthesis,
namely stability, and $k$-connectedness that states
that VTS remains connected after removing any $k-1$ edges.
%
In order to synthesize the parts of a VTS such that it satisfies the
constraints, we encode the synthesis problem into a satisfiability of
quantified Boolean formulas(QBFs). 
%

We have implemented the encoding in a highly flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on two found-in-nature VTSs, namely
M1~\cite{} and S1~\cite{}.
%
We have also applied our tool on various synthetic examples to
demonstrate that our tool scale upto the graph size ??, which
is the size of typical VTSs in a eukaryotic cell.

The following are the contributions of this work:
\begin{itemize}
\item We have identified an interesting application of
  the synthesis technology.
\item We have developed encoding of the synthesis problem in QBF.
\item A user friendly and scalable tool based on well known SMT solver Z3
\end{itemize}

The rest of the paper is organized as follows.
%
In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
constraints on VTSs.
%
In section~\ref{sec:prelim}, we present the synthesis problems and their
encoding into QBF satisfiability.
%
In section~\ref{sec:experiments}, we present our implementation and experimental results.
%
We discuss related work in~\ref{sec:related} and conclude in section~\ref{sec:conclusion}.

### 2018-04-23 papers/synth/prelim.tex
asd

We will also consider several variations of the model.
%
For example, unique edge between two nodes, activity of molecules is
not constrained by $\nodef$ and $\edgef$, etc.
%

A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
%
For a molecule $m \in M$,
an {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
each $ 0 < i < \ell$.
%
A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
$n,...,n'$ in $G$.
%
% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
% $m$-path $n,...,n'$ in $G$.
%
We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
$n$ is $m$-reachable from $n'$.
%
An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
if there are molecules $m,m' \in \mols$ such that $m$ is active in
$(n,M',n')$, $m'$ is active in $n'$, and $(m,m') \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with non-empty fusing molecules $M'' \subseteq M'$
and $\pairs(M'')$ are not active in any other node.
%
We call $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ is reachable from $n$ in $G$.
%
We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.
%
In the definition, we do not care about the paths to be $m$-connected for some $m$.  
%
A variant of the definition may be sensitive to the $m$-connectedness, but
we are not considering the variation.

\paragraph{Search problem}
Based upon earlier discussion, we need to answer the following search
question among VTSs.
For a given $k$, size $\nu$, and molecule number $\mu$,
we are searching for well-structured, stable, and well-fused VTS
$G = (\nodes,\mols,\edges,\nlabel,\pairs,\edgef,\nodef)$ such that
$|\nodes| = \nu$, $|\mols| = \mu$, and
$G$ is not $k$-connected.

\subsection{Boolean satisfiability of the search problem}

We translate the search problem into a Boolean satisfiability
problem and use SMT solvers to find the satisfying VTSs.
%
We will first present the variables used to encode the
VTSs and the properties.
%
Afterwards, we will present the constraints corresponding to the
properties.

\subsubsection{Variables for VTS description}
%
We assume that size of the graph is $\nu$ and number of molecules is
$\mu$.
%
Furthermore, we also limit the maximum number $\pi$ of edges present
between two nodes.
%
Here, we list the vector of Boolean variables and uninterpreted function symbols
that encode the VTSs.
\begin{enumerate}

\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
\item Boolean variable $p_{m,m'}$ indicates if $(m,m') \in \pairs$
\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
encoding $\nodef(m)$ map
\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
encoding $\edgef(m)$ map
\end{enumerate}
We also have auxiliary Boolean variables that will help us encode the well-fused and stability properties 
\begin{enumerate}
\item $a_{i,m}$ indicates that molecule $m$ is active at node $i$, i.e., $\nodef(m,L(i))$
  holds
\item $b_{i,j,q,m}$ indicates that molecule $m$ is active at $q$th edge $(i,M',j)$ between $i$ and $j$, i.e., $\edgef(m,M')$ holds
\item $r_{i,j,m,p}$ indicates if there is an $m$-path from
  $i$ to $j$ of length less than or equal to $p$
\end{enumerate}
For $k$-connected property, we also use the following auxiliary Boolean variables
\begin{enumerate}
\item $d_{i,j,q}$ indicates $q$th edge between $i$ and $j$ is dropped
\item $r'_{i,j}$ indicates if there is a path from $i$ to $j$ in the modified VTS
\end{enumerate}

We will describe the Boolean constraints that encode VTSs in several categories.
%
In the end, we will present in a table the constraints needed for the
model variants.
%
To avoid cumbersome notation, we will not explicitly write the ranges of the indexing
in the constraints.
%
$i$ and $j$ will range over nodes.
%
$m$ will range over molecules.
%
$q$ will range over edges between two nodes, i.e., from $1$ to $\pi$.
%

\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
%
We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
to encode the basic structure of VTSs.
%
For an edge to exist it should have one molecule present. 
%
\begin{align}
  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
\end{align}
If a molecule is active on an edge, it should be present on the edge.
%
\begin{align}
  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
\end{align}
A molecule should be present to be active on a node.  
\begin{align}
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  \tag{V3}\label{eq:c4}
\end{align}
The edge labels are subset of the node labels of the source and target nodes.
\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
\end{align}
Self edges are not allowed. 
\begin{align}
   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
\end{align}
We fix first half as Q-SNAREs and rest as R-SNAREs and set diagonal blocks in pairing matrix to be 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
\begin{align}
  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
  \tag{V6}\label{eq:c3}
\end{align}

\subsubsection{Well-fused constraints}
Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
its destination node.
%
Constraint~\eqref{eq:fuse2} encodes that each edge should not
be able to potentially fuse with any node other than its destination node.
\begin{align}
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies \bigvee_{m,m^{\prime}} (b_{i,j,q,m} \land a_{j,m^{\prime}} \land p_{m,m^{\prime}})
  \tag{V7}\label{eq:fuse1}  \\
\bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies \neg \bigvee_{j \neq j^{\prime}, m^{\prime\prime}} ( a_{j^{\prime},m^{\prime\prime}} \land p_{m,m^{\prime\prime}})
  \tag{V8}\label{eq:fuse2}  
\end{align}

% Fusion rules consist of two different mechanisms.
% \begin{enumerate}
% \item  A \textbf{pairing mechanism} which determines compatible Q-R pairs on vesicles and compartments that can cause fusion.
% \item \textbf{regulatory mechanisms} on the edges and nodes (possibly distinct) which regulates molecules activity based on the presence/absence of other molecules on the corresponding node or edge.
% \end{enumerate}
% Boolean constraint~\eqref{eq:fuse1} and~\eqref{eq:fuse2} are used to encode well-fused
% property.

% F4: For an edge to be valid, at least one SNARE pair on the vesicle and target compartment must be active and have a non-zero entry in the pairing matrix.

% F5: To ensure that fusion respects the graph structure by the edge under consideration, it should not be possible to fuse with any other node.

\subsubsection{Regulation on nodes and edges}
We are considering several models that differ in constraints on
the activity of molecules.
%
We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
the varying constraints.
%
The following constraint encodes no conditions on activities on nodes,
i.e., all the present molecules on the nodes are active.
\begin{align}
\bigwedge\limits_{i,m} n_{i,m} = a_{i,m}    \tag{Ann}\label{eq:ann}
\end{align}
The following constraint encodes that activity of a molecule $m$ on the node is
defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
\begin{align}
\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
\tag{Anb}\label{eq:anb}
\end{align}
The following constraint encodes no conditions on activities on edges,
i.e., all the present molecules on the edges are active.
\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
\tag{Aen}\label{eq:aen}
\end{align}
The following constraint encodes that activity of a molecule $m$ on the edge is
defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
\begin{align}
   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
  \tag{Aeb}\label{eq:aeb}
\end{align}
%
The following constraint encodes that the activity of the molecules on
edges is defined by inhibition by other molecules based on the pairing
matrix. 
\begin{align}
   \bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \limplies  \bigwedge_{m' \neq m} (p_{m,m'} \limplies e_{i,j,q,m'})] \lequiv (\neg b_{i,j,q,m} \land\;\;\;\;  \bigwedge_{\mathclap{m' \neq m, p_{m,m'}}} \neg b_{i,j,q,m'})
  \tag{Aep}\label{eq:aep}
\end{align}
%
\subsubsection{Constraints for stability condition}
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
\begin{align}
  \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
  \tag{R1}\label{eq:reach1}
\end{align}
Now we can encode stability using the reachability variables.
and say if there is an $m$-edge between $i$ and $j$, there is
$m$-reachable path from $j$ to $i$.
\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
  \tag{R2}\label{eq:reach2}
\end{align}

% Boolean variable
% F3 and F2 are used to model these constraints.

% % \textbf {Reachability definition and stability condition.}
% We have encoded stable condition by using reachability definition. \newline

% F3: Stability condition. For every leaving molecule, the source node is reachable from the target node with that molecule present, in maximum p steps.

% F2: Reachability definition. Node j is reachable from node i with kth molecule present in maximum p steps if either there is a direct edge between i-j with that molecule present or there is a direct edge between $i^{\prime \prime}$ $(i \neq i^{\prime \prime})$ and j with kth molecule present on that edge and $i^{\prime \prime}$ are reachable from i in p steps.

\subsubsection{$k$-connectivity constraints}
To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
%
Constraints~\ref{eq:drop1}-\ref{eq:drop4}
encode the relevant constraints for reachability
in the modified VTS. 
%
The following constraints encode that only
existing edges can be dropped and exactly $k-1$ edges are dropped.
\begin{align}
  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \tag{D1}\label{eq:drop1}\\
  \sum_{i,j,q} d_{i,j,q} = k-1
  \tag{D2}\label{eq:drop2}
\end{align}
We need to define reachability in the modified VTS, therefore we use
a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
In the following constraint, we encode $r'_{i,j}$ is true if there is an
edge $(i,\_,j)$ and it is not dropped, or there is a node
$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
not dropped and $r'_{i',j}$ is true.
\begin{align}
\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}  
  \tag{D3}\label{eq:drop3}
\end{align}
Since we search for disconnected modified VTS,
the following constraint encodes that there are 
unreachable pair of nodes in the underlying undirected graph.
% nodes such that
% there is no path between them .
\begin{align}
   \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
  \tag{D4}\label{eq:drop4}
\end{align}

The key improvement in our work over the earlier tool is the
encoding of reachability, which was done using enumeration of paths.
%
In the current work, we have encoded reachability in two different
ways in constraints~\eqref{eq:reach1} and~\eqref{eq:drop3}.
%
The reachability is recursively defined in~\eqref{eq:drop3} and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~\eqref{eq:drop4} and we find
only the solutions that captures the evidence of unreachability.
%
On the other hand,
we have added length of paths in our reachability encoding in constraint~\eqref{eq:reach1},
which needs relatively more auxiliary variables.
%
This is because constraint~\eqref{eq:reach2} has only positive
occurrences of the reachability variables and if we had defined
$r$s in ~\eqref{eq:reach1} without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

% We can go down or up using -C \_ option.  \newline

\subsection{Complete formula}
The complete QBF looks like the following.
\begin{align}
\exists \, e_{i,j,q} \forall \,d_{i,j,q}, r^{\prime}_{i,j,q} \, (D1 \land D2 \land D3 \land D4)  \, \land \notag\\  \forall\, n_{i,k}, a_{i,k}, e_{i,j,k,q}, b_{i,j,k,q}, r_{i,j,k}, p_{k,k^{\prime}} \, \neg (V1 \land V2 \land ... V8 \land A_{n} \land A_{e})  \label{eq:final}
\end{align}

\subsection{SMT problems for different variants}
%\ankit{Bring model variant table here}

We have encoded the following variants of VTSs.
%
The variants are due to different combinations of constraints on the
activity of molecules on the nodes and edges.
%
\begin{enumerate}[label=\Alph*]
\item Every present molecule is considered to be active.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules. 
\item Activity of molecules on the edges is based on Boolean function of presence of other molecules
\item Activity of molecules both on the edges and nodes is based on Boolean function of presence of other molecules.
\item Activity of molecules on the edges is driven by pairing inhibition.
\item Activity of molecules on the nodes is based on Boolean function of presence of other molecules and on edge by pairing inhibition.
\end{enumerate}
%
% For the version A, every present molecule is in active state.
%
In the table~\ref{tab:grph}, we present the constraints involved in each version.
%
The column two of the table shows that the constraints V1-V8, R1-R2, and D1-D4 are present
for every variant.
%
The column three of the table lists the constraints that are different among the variants.
%
%
One of the restriction is where the activity of the present molecule is dependent on the presence of the other molecules.
%
For example in version B, D, F activity of the molecules on the node is a boolean function of the presence of other molecules on that node; Anb.
%
Similarly for the case of the edge in version C and D; Aeb.
%
In the case of versions F the activity of the molecules on the edges
is described by pairing matrix; Aep.

%if all the pairs of the present molecule are present on the same edge than all of them inhibit each other resulting in making all the molecules inactive, we term this process ``pairing inhibition".
%
The constraints for the variants can be given to a SMT solver to find
VTSs that belong to the variants.

% We have applied the tool for the above variations for searching the
% VTSs that satisfies their corresponding properties. 
%
% After creating the constraint using different Boolean variables 
% we ship them directly to the solver.
% %
% In case of a satisfying (SAT) assignment of the added constraints the
% Z3 theorem prover gives a model with the variable assignment.
% %
% In case no possible satisfying assignment the solver returns UNSAT.

%
%

% \subsection{Creating a solver and solving these constraints}
% We will create a solver and add these build constraint using these constraints to that and then check whether there a satisfiable assignment that satisfies all these constraints.

% \begin{figure}[ht]
% %\vspace{-3mm}
% \begin{verbatim}
% # Create a solver
% s = Solver()
% # Add these constraints to it.
% s.add(A0, A1, C0, C1, C2, C4, C5, F0, F1, F2, F3, F4, F5, D0, D1, D2, D3)

% # Check for the satisfiability assignment.
% print s.check()   
% \end{verbatim}
% \caption{Solving for these constraints.}
% \label{code:motivate}
% \end{figure}

%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

>>>>

% We will also consider several variations of the model.
% %
% For example, unique edge between two nodes, activity of molecules is
% not constrained by $\nodef$ and $\edgef$, etc.
%

A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
%
For a molecule $m \in M$,
an {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
each $ 0 < i < \ell$.
%
A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
$n,...,n'$ in $G$.
%
% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
% $m$-path $n,...,n'$ in $G$.
%
We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
$n$ is $m$-reachable from $n'$.
%
An edge $(n,M',n') \in \edges$ {\em fuses} with its destination node $n'$
if there are molecules $m,m' \in \mols$ such that $m$ is active in
$(n,M',n')$, $m'$ is active in $n'$, and $(m,m') \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with non-empty fusing molecules $M'' \subseteq M'$
and $\pairs(M'')$ are not active in any other node.
%
We call $G$ {\em connected} if for each $n,n' \in \nodes$,
$n'$ is reachable from $n$ in $G$.
%
We call $G$ $k$-connected if for each $\edges' \subseteq \edges$ and $|\edges'| < k$,
VTS $(\nodes,\mols,\edges-E',\nlabel,\pairs,\edgef,\nodef)$ is connected.

%
% In the definition, we do not care about the paths to be $m$-connected for some $m$.  
% %
% A variant of the definition may be sensitive to the $m$-connectedness, but
% we are not considering the variation.

\subsection{Encoding VTS}

The conditions on the VTSs for a given size can be encoded as a QBF formula
with uninterpreted functions.
%
To encode the constraints, we need needs variables for each aspect of
VTS.
%
Let us suppose that the size of the graph is $\nu$ and number of
molecules is $\mu$.
%
Furthermore, we also limit the maximum number $\pi$ of edges present
between two nodes.
%
Here, we list the Boolean variables and uninterpreted function symbols
that encode the VTSs.
\begin{enumerate}

\item Boolean variable $n_{i,m}$ indicates if $m \in \nlabel(i)$
\item Boolean variable $e_{i,j,q}$ indicates if $q$th edge exists between $i$ and $j$.
\item Boolean variable $e_{i,j,q,m}$ indicates if $q$th edge between $i$ and $j$ contains $m$.
\item Boolean variable $p_{m,m'}$ indicates if $(m,m') \in \pairs$
\item uninterpreted Boolean functions $\nodef_m : \booleans^\mu \maps \booleans$
encoding $\nodef(m)$ map
\item uninterpreted Boolean functions $\edgef_m : \booleans^\mu \maps \booleans$
encoding $\edgef(m)$ map
\end{enumerate}

\subsection{Solvers}
Due the combinatorial nature of the graphs, the search space is huge
and often hard to enumerate naively.
%
We need sophisticated solvers
